Lab2

### 2021-08-02 src/data/DataCleaning.Rmd

```{r read in data, echo=FALSE}
d_covid <- read.csv(url('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties-recent.csv'))
d_openings <- read.csv(file = './../../data/raw/COVID-19 US state policy database (CUSP) - Closures & Reopening.csv')
d_trips <- read.csv(file = './../../data/raw/Trips_by_Distance.csv')
```

@@

# dates under investigation
start_date = as.Date("2021-06-01")
end_date = as.Date("2021-06-30")
```

```{r clean covid data, echo=FALSE}
# COVID-19 data
# filters by date/state
d_covid <- d_covid %>%
  mutate(
    date = as.Date(date)
  ) %>%
  filter(
    date >= start_date, date <= end_date,
    grepl(paste(state_id, collapse = "|"), state)
  )

# aggregate county data
d_covid <- d_covid %>%
  group_by(fips) %>%
  mutate(
    sum_cases = sum(cases),
    sum_deaths = sum(deaths),
    state = state.abb[match(state, state.name)]
  ) %>%
  select(
    county, state, fips, sum_cases, sum_deaths
  ) %>%
  distinct(fips, .keep_all = TRUE)
```

@@

# filters by date/state
d_trips <- d_trips %>%
  mutate(
    Date = as.Date(Date)
  ) %>%
  filter(
    Date >= start_date, Date <= end_date,
    grepl(paste(state_id, collapse = "|"), State.Postal.Code)
  )

>>>>

```{r read in data, echo=FALSE}
d_covid <- read.csv(url('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv'))
d_openings <- read.csv(file = './../../data/raw/COVID-19 US state policy database (CUSP) - Closures & Reopening.csv')
d_trips <- read.csv(file = './../../data/raw/Trips_by_Distance.csv')
```

@@

# dates under investigation
start_date = as.Date("2021-06-01")
end_date = as.Date("2021-06-30")

# start_date = as.Date("2021-06-01")
# end_date = as.Date("2021-06-30")
```

```{r clean covid data, echo=FALSE}
# COVID-19 data
# filters by date/state
d_covid <- d_covid %>%
  mutate(
    date = as.Date(date)
  ) %>%
  filter(
    (date >= start_date & date <= end_date),
    grepl(paste(state_id, collapse = "|"), state)
  )

# max county data (cases and deaths are cumulative)
d_covid <- d_covid %>%
  group_by(fips) %>%
  mutate(
    cases = max(cases) - min(cases),
    deaths = max(deaths) - min(cases),
    state = state.abb[match(state, state.name)]
  ) %>%
  select(
    county, state, fips, cases, deaths
  ) %>%
  distinct(fips, .keep_all = TRUE)
```

@@

# filters by date/state
d_trips <- d_trips %>%
  mutate(
    Date = as.Date(Date)
  ) %>%
  filter(
    (Date >= start_date & Date <= end_date),
    grepl(paste(state_id, collapse = "|"), State.Postal.Code)
  )
